### 2014-08-04 paper/paper.tex
Wrote a bunch for future work

%TODO Feature Selection
%TODO mention bag of words

@@

% TODO expand on document frequency

@@

            \item By \textbf{Removing Stopwords}, words that do not
                discriminate between classes are eliminated. Because of the
                limited size of the dataset only 28 stopwords are used.

            \item Then \textbf{Uncommon words} are removed. Words that do not
                meet a certain document frequency threshold are eliminated.
                Many of these words are proper nouns that, if retained are
                likely to cause the classifier to overfit to the training set.

@@

% TODO Write something here about uncommon not getting performance gains
% without normalization

\begin{figure}[H]
    \begin{center}
    \includegraphics[scale=0.75]{figures/maxent_boxplot.png}
    \caption{Caption...}
    \label{figure:maxent}
    \end{center}
\end{figure}

@@

\begin{figure}[H]
    \begin{center}
    \includegraphics[scale=0.75]{figures/bayes_boxplot.png}
    \caption{Caption...}
    \label{figure:bayes}
    \end{center}
\end{figure}

@@

@@

@@

%TODO

>>>>

In order to perform text classification of any kind one of the most important
aspects is deciding how to represent a document and how to select
representative features. A document is often represented as either a
\textit{bag-of-words} or \textit{string}. For the limited time frame of this
project the \textit{bag-of-words} method was used.

There are many established methods of selecting features such as document
frequency, which is simply the number of documents that a word occurs at least
once in. Document frequency has the added benefit of not requiring a class
labels to select features. While document frequency is the only method employed
for this project many other method exist, such as Gini Index, Information Gain,
and $\chi^{2}$-statistic \cite{Aggarwal2012}. Each of these more complex
methods rely on the class label in the training set in order to determine how
well the feature discriminates between classes.

@@

@@

            \item By \textbf{Removing Stopwords}, words that do not
                discriminate between classes are eliminated. Because of the
                limited size of the dataset only 28 stopwords are used. For a
                full list of stopwords see section \ref{ssection:stopwords}

            \item Then \textbf{Uncommon words} are removed. Words that do not
                meet a certain document frequency threshold are eliminated.
                Many of these words are proper nouns that, if retained are
                likely to cause the classifier to overfit to the training set.
                A threshold of one was used throughout the testing process.

@@

\begin{figure}[H]
    \begin{center}
    \includegraphics[scale=0.75]{figures/maxent_boxplot.png}
    \caption{This boxplot shows the F-score of each of twenty folds in all five
    Maximum Entropy experiments}
    \label{figure:maxent}
    \end{center}
\end{figure}

@@

\begin{figure}[H]
    \begin{center}
    \includegraphics[scale=0.75]{figures/bayes_boxplot.png}
    \caption{This boxplot shows the F-score of each of ten folds in all five
    Naive Bayes experiments}
    \label{figure:bayes}
    \end{center}
\end{figure}

@@

The top solution from the National Research Council of Canada made use of a
Hashtag lexicon that they developed between April of 2012 and December of the
same year \cite{Mohammad2013}. The final \textit{NRC Hashtag Sentiment Lexicon}
has more than 350,00 entries and is available at
\href{http://www.saifmohammad.com/WebDocs/NRC-Hashtag-Sentiment-Lexicon-v0.1.zip}{Saif
Mohammad's website}.

@@

\subsubsection{Negation}
\label{sssection:negation}
%TODO
\subsubsection{N-gram Features}
\label{sssection:ngram}
%TODO
\subsubsection{Employing Sentiment Lexicon}
\label{sssection:sentimentlexicon}

Many of the more complex solutions submitted to the SemEval-2013 workshop made
uses of sentiment lexicons that capture a term's polarity. These lexicons, such
as \href{http://sentiwordnet.isti.cnr.it/}{SentiWordNet}, express the positive,
neutral, and negative sentiment of each homonym.

@@

Many of the top solutions submitted to the workshop such as NRC-Canada
\cite{Mohammad2013} made use of a support vector machine for classification.
This indicates that when used effectively a SVM solution can out-perform a
Maximum Entropy solution. The KLUE team on the other hand found that their
Maximum Entropy solution outperform their linear SVM solution
\cite{Proisl2013}.
